The SMT Competition 2015--2018

### 2018-11-22 2018/report/SMT-COMP.tex
Tables with winners

\author{%
  \name{Tjark Weber (competition chair, 2015--2018)}
  \email{tjark.weber@it.uu.se} \\
  \addr Uppsala University \\
  Uppsala \\
  Sweden
  \AND
  \name{Sylvain Conchon (co-organizer, 2015--2016)}
  \email{Sylvain.Conchon@lri.fr} \\
  \addr Affiliation \\
  City \\
  Country
  \AND
  \name{David D\'{e}harbe (co-organizer, 2015--2016)}
  \email{david@dimap.ufrn.br} \\
  \addr Federal University of Rio Grande do Norte \\
  Natal \\
  Brazil
  \AND
  \name{Matthias Heizmann (co-organizer, 2016--2018)}
  \email{heizmann@informatik.uni-freiburg.de} \\
  \addr Affiliation \\
  City \\
  Country
  \AND
  \name{Aina Niemetz (co-organizer, 2018)}
  \email{niemetz@cs.stanford.edu} \\
  \addr Stanford University\\
  Stanford \\
  USA
  \AND
  \name{Giles Reger (co-organizer, 2017--2018)}
  \email{giles.reger@manchester.ac.uk} \\
  \addr Affiliation \\
  City \\
  Country}

@@

>>>>

\author{%
  \name{Tjark Weber (competition chair, 2015--2018)}
  \email{tjark.weber@it.uu.se} \\
  \addr Uppsala University \\
  Uppsala \\
  Sweden
  \AND
  \name{Sylvain Conchon (co-organizer, 2015--2016)}
  \email{Sylvain.Conchon@lri.fr} \\
  \addr Affiliation \\
  City \\
  Country
  \AND
  \name{David D\'{e}harbe (co-organizer, 2015--2016)}
  \email{david.deharbe@clearsy.com} \\
  \addr ClearSy Systems Engineering \\
  Aix-en-Provence \\
  France
  \AND
  \name{Matthias Heizmann (co-organizer, 2016--2018)}
  \email{heizmann@informatik.uni-freiburg.de} \\
  \addr Affiliation \\
  City \\
  Country
  \AND
  \name{Aina Niemetz (co-organizer, 2018)}
  \email{niemetz@cs.stanford.edu} \\
  \addr Stanford University\\
  Stanford \\
  USA
  \AND
  \name{Giles Reger (co-organizer, 2017--2018)}
  \email{giles.reger@manchester.ac.uk} \\
  \addr Affiliation \\
  City \\
  Country}

@@

In tables~\ref{tab:winners-main-1},~\ref{tab:winners-main-2} and
~\ref{tab:winners-unsat-core}, entries $A/B$ indicate that solver $A$
is the winner considering sequential performance, while $B$ is the
winner considering parallel performance. When the same solver has won
both, which is most often the case, its name appears just once. All
runs in the application track are sequential and therefore only
sequential performance is used to determine the winners.

\include{table-winners-main}

\include{table-winners-application}

\include{table-winners-unsat-core}
